---
title: "Penguin"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Load packages and read-in penguins.csv data

```{r, include = FALSE}
library(tidyverse)
library(car)
library(onewaytests)

penguins <- read_csv("penguins.csv")
```

2. Do some exploring

Our question: 
Is there a sig difference in mean flipper length for female penguins by species (Chinstrap, Gentee, Adelie)?

Should we use ANOVA? - have 3 species 

First, do some exploring.

New functions: with + table for easy counting over multiple factors
Update species name using case_when
```{r}
counts <- with(penguins, table(species, sex))

penguins2 <- penguins %>% 
  mutate(common_name = 
           case_when(
             species =="Chinstrap penguin (Pygoscelis antarctica)" ~ "Chinstrap",
             species =="Gentoo penguin (Pygoscelis papua)" ~ "Gentoo",
             species =="Adelie Penguin (Pygoscelis adeliae)" ~ "Adelie"
           )) %>% 
  select(-species) %>% 
  filter(sex == "FEMALE")
```

-Exploratory Graphs
-Summary stats
-Levene's tests for equal variance
-One way ANOVA
-Post hoc testing

```{r}
#Exploratory graphs
hists <- ggplot(penguins2, aes(x = flipper_length))+
  geom_histogram(aes(fill = common_name))+
  facet_wrap(~common_name)
hists

qqplot <- ggplot(penguins2, aes(sample = flipper_length))+
  geom_qq()+
  facet_wrap(~common_name)
qqplot

#Levene's test for equal variance (> 2 groups... if you have two groups, use the F test for equal variances)
#We'll use the function leveneTest from the 'car' package to do this 

#H0: Variances are equal
#HA: Variances are unequal

penguin_levene <- leveneTest(flipper_length ~ common_name, data = penguins2)
penguin_levene #We retain the null hyp of equal variance (p = 0.06)

# OR: Is larger variance greater than 4x the smaller?

variance_table <- penguins2 %>% 
  group_by(common_name) %>% 
  summarize(
    Variance= var(flipper_length))
variance_table

#No, variance is not 4x greater, so we assume equal variance
```

3. One-way ANOVA

Now we have tested all the assumptions necessary to perform an ANOVA.

Factor: common_name (species)
Levels: 3 (Chinstrap, Gentoo, Adelie)
Random variable: flipper_length (mm)

Is there a sig dif in mean flipper length (mm) for female penguin species?

Two ways to do this: 1)
```{r}
# H0: No sig difference in mean flipper length b/w species
# HA: At least one difference in mean flipper length

penguin_aov <- aov(flipper_length ~ common_name, data = penguins2)
summary(penguin_aov)
#p < 0.05

#If these samples all come from the same population, it is highly unlikely that we would get sample means at least this different 
#At least two samples were taken from populations with different means. Which are different?

```

Mean flipper lengths for Adelie, Gentoo, and Chinstrap penguins are significantly different (F(df) = statistic, p < 0.001, $\alpha$ = 0.05)

But at this point this is kind of misleading....

4. Post-hoc testing using Tukey's HSD

```{r}
penguin_ph <- TukeyHSD(penguin_aov)
penguin_ph
```

Mean flipper lengths for Adelie, Gentoo, and Chinstrap penguins are all significantly different from each other (F(df) = statistic, p < 0.001, $\alpha$ = 0.05, with post-hoc Tukey's HSD, $\alpha$ = 0.05 ).



