---
title: "Penguin"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Load packages and read-in penguins.csv data

```{r, include = FALSE}
library(tidyverse)
library(car)
library(onewaytests)

penguins <- read_csv("penguins.csv")
```

2. Do some exploring

Our question: 
Is there a sig difference in mean flipper length for female penguins by species (Chinstrap, Gentee, Adelie)?

Should we use ANOVA? - have 3 species 

First, do some exploring.

New functions: with + table for easy counting over multiple factors
Update species name using case_when
```{r}
counts <- with(penguins, table(species, sex))

penguins2 <- penguins %>% 
  mutate(common_name = 
           case_when(
             species =="Chinstrap penguin (Pygoscelis antarctica)" ~ "Chinstrap",
             species =="Gentoo penguin (Pygoscelis papua)" ~ "Gentoo",
             species =="Adelie Penguin (Pygoscelis adeliae)" ~ "Adelie"
           )) %>% 
  select(-species) %>% 
  filter(sex == "FEMALE")
```

-Exploratory Graphs
-Summary stats
-Levene's tests for equal variance
-One way ANOVA
-Post hoc testing

